---
title: "R-programing"
author: "ZeesZerro"
date: "20 กรกฎาคม 2560"
output: html_document
---

Install package
```{r}
install.packages(c("MASS", "httr", "XML", "xml2", "ggplot2", "ggplot2movies", "plyr", "curl", "rvest", "data.table"))
```

load library
```{r}
library(MASS)
```

show data
```{r}
View(birthwt)
View(Cars93)
```

change colname
```{r}
colnames(birthwt) <- c("birthwt.below.2500", "mother.age", "mother.weight", 
    "race", "mother.smokes", "previous.prem.labor", "hypertension", "uterine.irr", 
    "physician.visits", "birthwt.grams")
```

load library
```{r}
library(plyr)
```


change value to text
```{r}
birthwt <- transform(birthwt, 
            race = as.factor(mapvalues(race, c(1, 2, 3), 
                              c("white","black", "other"))),
            mother.smokes = as.factor(mapvalues(mother.smokes, c(0,1), c("no", "yes"))),
            hypertension = as.factor(mapvalues(hypertension, 
                              c(0,1), c("no", "yes"))),
            uterine.irr = as.factor(mapvalues(uterine.irr, 
                              c(0,1), c("no", "yes")))
            )
```

change value in visit, if visit >= 3 then visit<-"3.or.more" and add new col phy.visit.binned to birthwt
```{r}
phys.visit.binned <- birthwt$physician.visits
phys.visit.binned[phys.visit.binned >= 3] <- "3.or.more"
birthwt <- transform(birthwt, phys.visit.binned = as.factor(phys.visit.binned))

birthwt$phys.visit.binned
```

install packgate
```{r}
install.packages(c("plot3D"))
```


load library
```{r}
library(ggplot2)
library(plot3D)
```

show (plot) graph
ไปดูตัวอย่างกราฟที่ https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf
```{r}
View(diamonds)
diamond.plot <-ggplot(data=diamonds, aes(x=carat, y=price,colour=color))
diamond.plot+geom_area()
```

```{r}
diamond.plot+geom_area()+facet_wrap(~ cut)
```

plot 3d
```{r}
par(mar=c(2,2,2,2))
par(mfrow=c(1,1))
R<-3
r<-2
x<-seq(0,2*pi,length.out = 50)
y<-seq(0,pi,length.out = 50)
M<-mesh(x,y)
alpha<-M$x
beta<-M$y

surf3D(x= (R+r*cos(alpha))*cos(beta), 
       y= (R+r*cos(alpha))*sin(beta), 
       z= r*sin(alpha), 
       colkey=FALSE, 
       bty="b2", 
       main="example Data 3d")
```

test data diamons
```{r}
par(mar=c(2,2,2,2))
par(mfrow=c(1,1))
R<-3
r<-2
x<-diamonds$carat
y<-diamonds$price
M<-mesh(x,y)
alpha<-M$x
beta<-M$y

surf3D(x= (R+r*cos(alpha))*cos(beta), 
       y= (R+r*cos(alpha))*sin(beta), 
       z= r*sin(alpha), 
       colkey=FALSE, 
       bty="b2", 
       main="example Data 3d")
```

